%*******************************************************
% Publications
%*******************************************************
\pdfbookmark[1]{Publicaciones}{Publicaciones Científicas}
\chapter*{Scientific Publications}
Algunas de las ideas, imágenes y datos mostrados en esta tésis han sido publicados previamente en las siguientes referencias:
\bigskip

\begin{itemize}
 \item \person{Pablo García-Sánchez, J. González, Pedro A. Castillo, Maribel García Arenas, Juan Julián Merelo Guervós} \emph{Service oriented evolutionary algorithms}.  Soft Comput. 17(6): 1059--1075 (2013).


% no metas estos del "companion", que todos sabemos lo que es... 

~\\

 \item \person{V\'ictor M. Rivas, J.J. Merelo, I. Rojas, G. Romero, P.A. Castillo,  J. Carpio} \emph{ Evolving two-dimensional fuzzy systems}, \textbf{Fuzzy Sets and Systems}, 2003; Factor de impacto: \textbf{0,577};\\

 \item \person{Jos\'e Carpio, Pablo Garc\'ia-S\'anchez, Antonio Miguel Mora, Juan Juli\'an Merelo Guerv\'os, Jes\'us Caraballo, Ferm\'in Vaz, Carlos Cotta} \emph{ Evolving the Strategies of Agents for the ANTS Game}. International Work-Conference on Artificial Neural Networks (IWANN)}, 2013
 
 \item \person{Pablo García-Sánchez, J. González, Pedro A. Castillo, Juan Julián Merelo Guervós, Antonio Miguel Mora, Juan Luís Jiménez Laredo, Maribel García Arenas} \emph{ A Distributed Service Oriented Framework for Metaheuristics Using a Public Standard}. In Proceeding of Nature Inspired Cooperative Strategies for Optimization. Studies in Computational Intelligence. Springer, 2010. p: 211--222.


 \item \person{P. García-Sánchez, A. Fernández-Ares, A. M. Mora, P. A. Castillo, J. González and J.J. Merelo} \emph{Tree depth influence in Genetic Programming for generation of competitive agents for RTS games}. Applications of Evolutionary Computation, EvoApplicatons 2010: EvoCOMPLEX, EvoGAMES, EvoIASP, EvoINTELLIGENCE, EvoNUM, and EvoSTOC, Proceedings. Springer, 2014. Lecture Notes in Computer Science (to appear).

 \item \person{P. García-Sánchez, A. M. Mora, P. A. Castillo, J. González and J.J. Merelo} \emph{A methodology to develop Service Oriented Evolutionary Algorithms}. Proceedings of 8th International Symposium on Intelligent Distributed Computing (IDC'2014) Springer, 2014. Studies in Computational Science (to appear).

\end{itemize}
